SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Typos in Sect.4.5.
|(ACT delta |x:sva_SV4:1:2| -> (ACT delta |x:sva_SV4:1:2|)

Here the behaviour of the hole ``$P$'' ($a_1$ in Example~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x_2)$) as ``|(ACT delta
|x:sva\_SV4:1:2|''. Line 16 requires that $a_1 = \delta(x_2)$ to match
the second synchronisation vector of the root pNet node, and lines
17-18 that $a_1$ does not match $\delta(x_1)$ for any $x_1$. 
We also display  the diagnosis (``SAT'' or ``UNSAT'') generated by Z3.

@@

In this section, we present \Simon {a variation of} the Failure Monitor architecture from the
CubETH nanosatellite on-board software
case-study~\cite{CubETH-case-study} realised using BIP.
The architecture-based design process in BIP takes as input a set of
components providing basic functionality of the system and a set of
temporal properties that must be enforced in the final system.  For
each property, a corresponding architecture is identified
and applied to the model, thereby potentially introducing additional
coordinator components and modifying the connectors that define
synchronisation patterns among ports of components.

>>>>

Here the behaviour of the hole ``$P$'' ($a_1$ in Example~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x_2)$) as ``(ACT delta
|x:sva\_SV4:1:2|)''. Line 16 requires that $a_1 = \delta(x_2)$ to match
the second synchronisation vector of the root pNet node, and lines
17-18 that $a_1$ does not match $\delta(x_1)$ for any $x_1$. 
We also display  the diagnosis (``SAT'' or ``UNSAT'') generated by Z3.

@@

In this section, we present \Simon {a variation of} the Failure Monitor architecture from the
CubETH nanosatellite on-board software
case-study~\cite{CubETH-case-study} realised using BIP.

The architecture-based design process in BIP takes as input a set of
components providing basic functionality of the system and a set of
temporal properties that must be enforced in the final system.  For
each property, a corresponding architecture is identified
and applied to the model, thereby potentially introducing additional
coordinator components and modifying the connectors that define
synchronisation patterns among ports of components.
